Metrics

### 2024-04-13 src/plots.Rmd
Clean up plots with overlapping labels

# Prepare boxplot data
agedata <- out %>%
    select(
        Model,
        `PCCC Adult Agreement`,
        `PCCC Child Agreement`,
        `PCCC Neo Agreement`,
        `CSMF Accuracy Adult Agreement`,
        `CSMF Accuracy Child Agreement`,
        `CSMF Accuracy Neo Agreement`
    ) %>%
    rename(
         Adult = `PCCC Adult Agreement`,
         Child = `PCCC Child Agreement`,
         Neonatal = `PCCC Neo Agreement`
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -c(
            Model,
            `CSMF Accuracy Adult Agreement`,
            `CSMF Accuracy Child Agreement`,
            `CSMF Accuracy Neo Agreement`
        ),
        names_to = "Age Group",
        values_to = "PCCC"
    ) %>%
    group_by(`Age Group`) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) + 0.05,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) - 0.05,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(
                Model, "\n(", round(PCCC, 2),
                ", CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Mid Value" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            PCCC,
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        )
    ) %>%
    mutate( # re-order age
        "Age Group" = factor(`Age Group`, levels = c(
            "Neonatal",
            "Child",
            "Adult"
        ))
    ) %>%
    mutate( # rename ages with counts
        "Age Group" = recode(`Age Group`, !!!age_remap)
    )

# Plot boxplot
ageplot <- agedata %>%
    ggplot(aes(x = `Age Group`, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_point(
        aes(y = `PCCC Mid Value`),
        shape = 1,
        size = 1.5,
        fill = "white",
        color = "darkgray",
        alpha = 0.8,
        position = position_nudge(x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.055)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2,
        hjust = 0,
        position = position_nudge(y = 0.055)
    ) +
    geom_text(
        aes(label = `PCCC Mid`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.025),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.025),
        size = 3
    ) +
    labs(
        x = paste0("Physician Agreed Records (n=", nagree, ", 100%)"),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.25, 0.9) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        plot.margin = margin(t = 16, b = 12, l = 12, r = 12),
        axis.line = element_line(color = "black"),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 10)),
        axis.line.x = element_line(
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        ),
        axis.line.y = element_blank()
    )

@@

    # Prepare boxplot data
    sxdata <- out %>%
        select(
            Model,
            starts_with(sprintf("PCCC %s Sex Agree", aref))
        ) %>%
        rename_at(
             vars(-Model),
             ~gsub(sprintf("PCCC %s Sex Agree ", aref), "", .)
        ) %>%
        filter(!str_detect(Model, "&")) %>% # remove multi models
        pivot_longer( # transform to long format
            cols = -Model,
            names_to = "Sex",
            values_to = "PCCC"
        ) %>%
        mutate( # rename cod with counts
            "Sex" = recode(Sex, !!!sex_remap)
        ) %>%
        group_by(Sex) %>%
        mutate( # Make values less than 0 equal to 0
            PCCC = if_else(PCCC <= 0, 0, PCCC)
        ) %>%
        mutate( # Add min, mid, and max model names to label
            "PCCC Min" = if_else(
                PCCC <= min(PCCC) + 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Max" = if_else(
                PCCC >= max(PCCC) - 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Mid" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                paste0(Model, "\n(", round(PCCC, 2), ")"),
                NA
            ),
            "PCCC Mid Value" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                PCCC,
                NA
            ),
            "PCCC Min" = if_else( # Combine into one row if close PCCC
                `PCCC` == min(PCCC),
                if_else(
                    sum(!is.na(`PCCC Min`)) > 1,
                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
                    paste0(
                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                        collapse = "\n"
                    )
                ),
                NA
            ),
            "PCCC Max" = if_else(
                `PCCC` == max(PCCC),
                if_else(
                    sum(!is.na(`PCCC Max`)) > 1,
                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                           collapse = "\n")
                ),
                NA
            )
        )

@@

    # Plot boxplot
    sxplot <- sxdata %>%
        ggplot(aes(x = Sex, y = PCCC)) +
        geom_boxplot(
            linewidth = 0.5,
            width = 0.25
        ) +
        geom_point(
            aes(y = `PCCC Mid Value`),
            shape = 1,
            size = 1.5,
            fill = "white",
            color = "darkgray",
            alpha = 0.8,
            position = position_nudge(x = -0.35)
        ) +
        geom_text(
            aes(label = `PCCC Min`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 1,
            position = position_nudge(y = -0.09)
        ) +
        geom_text(
            aes(label = `PCCC Mid`),
            color = "#4d4d4d",
            size = 2,
            hjust = 1,
            position = position_nudge(y = -0.025, x = -0.35)
        ) +
        geom_text(
            aes(label = `PCCC Max`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 0,
            position = position_nudge(y = 0.09)
        ) +
        stat_summary( # min pccc txt on boxplot
            geom = "text",
            fun = min,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = -0.04),
            size = 3
        ) +
        stat_summary( # max pccc txt on boxplot
            geom = "text",
            fun = max,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = 0.04),
            size = 3
        ) +
        labs(
            x = atitle,
            y = "PCCC (0=Low, 1=High)"
        ) +
        ylim(0.1, 1) +
        coord_flip() +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.line = element_blank(),
            axis.line.y = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.line.x = element_line(
                color = "black",
                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
            )
        )

>>>>

# Prepare boxplot data
agedata <- out %>%
    select(
        Model,
        `PCCC Adult Agreement`,
        `PCCC Child Agreement`,
        `PCCC Neo Agreement`,
        `CSMF Accuracy Adult Agreement`,
        `CSMF Accuracy Child Agreement`,
        `CSMF Accuracy Neo Agreement`
    ) %>%
    rename(
         Adult = `PCCC Adult Agreement`,
         Child = `PCCC Child Agreement`,
         Neonatal = `PCCC Neo Agreement`
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -c(
            Model,
            `CSMF Accuracy Adult Agreement`,
            `CSMF Accuracy Child Agreement`,
            `CSMF Accuracy Neo Agreement`
        ),
        names_to = "Age Group",
        values_to = "PCCC"
    ) %>%
    group_by(`Age Group`) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) + 0.05,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) - 0.05,
            paste0(
                Model, "\n(",
                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(round(PCCC, 2), ", "), ""),
                "CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(
                Model, "\n(", round(PCCC, 2),
                ", CSMF=", round(case_when(
                    `Age Group` == "Adult"  ~ `CSMF Accuracy Adult Agreement`,
                    `Age Group` == "Child"  ~ `CSMF Accuracy Child Agreement`,
                    `Age Group` == "Neonatal"  ~ `CSMF Accuracy Neo Agreement`
                ),2), ")"),
            NA
        ),
        "PCCC Mid Value" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            PCCC,
            NA
        ),
        "PCCC Mid Left" = if_else(
          `PCCC Mid Value` <= 0.5,
          `PCCC Mid`,
          NA
        ),
        "PCCC Mid Right" = if_else(
          `PCCC Mid Value` > 0.5,
          `PCCC Mid`,
          NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\,\\s*", "\n("),
                    collapse = "\n"
                )
            ),
            NA
        )
    ) %>%
    mutate( # re-order age
        "Age Group" = factor(`Age Group`, levels = c(
            "Neonatal",
            "Child",
            "Adult"
        ))
    ) %>%
    mutate( # rename ages with counts
        "Age Group" = recode(`Age Group`, !!!age_remap)
    )

# Plot boxplot
ageplot <- agedata %>%
    ggplot(aes(x = `Age Group`, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_point(
        aes(y = `PCCC Mid Value`),
        shape = 1,
        size = 1.5,
        fill = "white",
        color = "darkgray",
        alpha = 0.8,
        position = position_nudge(x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.055)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2,
        hjust = 0,
        position = position_nudge(y = 0.055)
    ) +
    geom_text(
        aes(label = `PCCC Mid Left`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Mid Right`),
        color = "#4d4d4d",
        size = 2,
        hjust = 0,
        position = position_nudge(y = 0.015, x = -0.3)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.025),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.025),
        size = 3
    ) +
    labs(
        x = paste0("Physician Agreed Records (n=", nagree, ", 100%)"),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.25, 0.9) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        plot.margin = margin(t = 16, b = 12, l = 12, r = 12),
        axis.line = element_line(color = "black"),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 10)),
        axis.line.x = element_line(
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        ),
        axis.line.y = element_blank()
    )

@@

    # Prepare boxplot data
    sxdata <- out %>%
        select(
            Model,
            starts_with(sprintf("PCCC %s Sex Agree", aref))
        ) %>%
        rename_at(
             vars(-Model),
             ~gsub(sprintf("PCCC %s Sex Agree ", aref), "", .)
        ) %>%
        filter(!str_detect(Model, "&")) %>% # remove multi models
        pivot_longer( # transform to long format
            cols = -Model,
            names_to = "Sex",
            values_to = "PCCC"
        ) %>%
        mutate( # rename cod with counts
            "Sex" = recode(Sex, !!!sex_remap)
        ) %>%
        group_by(Sex) %>%
        mutate( # Make values less than 0 equal to 0
            PCCC = if_else(PCCC <= 0, 0, PCCC)
        ) %>%
        mutate( # Add min, mid, and max model names to label
            "PCCC Min" = if_else(
                PCCC <= min(PCCC) + 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Max" = if_else(
                PCCC >= max(PCCC) - 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Mid" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                paste0(Model, "\n(", round(PCCC, 2), ")"),
                NA
            ),
            "PCCC Mid Value" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                PCCC,
                NA
            ),
            "PCCC Mid Left" = if_else(
                `PCCC Mid Value` <= 0.5,
                `PCCC Mid`,
                NA
            ),
            "PCCC Mid Right" = if_else(
                `PCCC Mid Value` > 0.5,
                `PCCC Mid`,
                NA
            ),
            "PCCC Min" = if_else( # Combine into one row if close PCCC
                `PCCC` == min(PCCC),
                if_else(
                    sum(!is.na(`PCCC Min`)) > 1,
                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
                    paste0(
                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                        collapse = "\n"
                    )
                ),
                NA
            ),
            "PCCC Max" = if_else(
                `PCCC` == max(PCCC),
                if_else(
                    sum(!is.na(`PCCC Max`)) > 1,
                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                           collapse = "\n")
                ),
                NA
            )
        )

@@

    # Plot boxplot
    sxplot <- sxdata %>%
        ggplot(aes(x = Sex, y = PCCC)) +
        geom_boxplot(
            linewidth = 0.5,
            width = 0.25
        ) +
        geom_point(
            aes(y = `PCCC Mid Value`),
            shape = 1,
            size = 1.5,
            fill = "white",
            color = "darkgray",
            alpha = 0.8,
            position = position_nudge(x = -0.35)
        ) +
        geom_text(
            aes(label = `PCCC Min`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 1,
            position = position_nudge(y = -0.09)
        ) +
        geom_text(
            aes(label = `PCCC Mid Left`),
            color = "#4d4d4d",
            size = 2,
            hjust = 1,
            position = position_nudge(y = -0.025, x = -0.35)
        ) +
        geom_text(
            aes(label = `PCCC Mid Right`),
            color = "#4d4d4d",
            size = 2,
            hjust = 0,
            position = position_nudge(y = 0.025, x = -0.35)
        ) +
        geom_text(
            aes(label = `PCCC Max`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 0,
            position = position_nudge(y = 0.09)
        ) +
        stat_summary( # min pccc txt on boxplot
            geom = "text",
            fun = min,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = -0.04),
            size = 3
        ) +
        stat_summary( # max pccc txt on boxplot
            geom = "text",
            fun = max,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = 0.04),
            size = 3
        ) +
        labs(
            x = atitle,
            y = "PCCC (0=Low, 1=High)"
        ) +
        ylim(0.1, 1) +
        coord_flip() +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.line = element_blank(),
            axis.line.y = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.line.x = element_line(
                color = "black",
                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
            )
        )
